Combined single-cell transcriptomics and virus sequencing of influenza infections that trigger innate immunity

### 2018-09-20 paper/paper.tex
organized mutant plasmid maps and fixed numbering of PB1del names

To generate an NS1-inactivated strain of influenza, six nucleotide changes resulting in the addition of five in-frame stop codons introduced immediately downstream of the 5' splice donor site, interrupting translation of NS1 while leaving NS2 (NEP) intact.
The viral RNA produced by this vector is described in (sequence)\abrcomment{I have uploaded the genbank files, just waiting for appropriate figure to append}.
This modified plasmid was used in a reverse-genetics approach to recapitulate mutant virus, harvesting transfection supernatant after 72h.
This virus was then passaged in MDCK-SIAT1 cells for 48h at an MOI of 0.05---due to slower growth kinetics than the wild-type virus this longer incubation was necessary.
Genome copy number of this virus relative to infectious titer was determined as described below by qPCR.

>>>>

To generate an NS1-inactivated strain of influenza, six nucleotide changes resulting in the addition of five in-frame stop codons starting 10 nucleotides downstream of the 5' splice donor site, interrupting translation of NS1 while leaving NS2 (NEP) intact.
The viral RNA produced by this vector is described in (sequence)\abrcomment{I have uploaded the genbank files, just waiting for appropriate figure to append}.
This modified plasmid was used in a reverse-genetics approach to recapitulate mutant virus, harvesting transfection supernatant after 72h.
This virus was then passaged in MDCK-SIAT1 cells for 48h at an MOI of 0.05---due to slower growth kinetics than the wild-type virus this longer incubation was necessary.
Genome copy number of this virus relative to infectious titer was determined as described below by qPCR.
